Refining from the VHDL-AMS Hardware Description Language to the BON High-level Specification Language

### 2010-05-25 papers/BON_VHDL/paper.tex
Author update and two writing tweaks.

\author{Joseph R. Kiniry and Dragan Stosic\\
UCD CASL: Complex and Adaptive Systems Laboratory and\\
School of Computer Science and Informatics,\\
University College Dublin,\\
Belfield, Dublin 4, Ireland,\\
kiniry@acm.org and dragan.stosic@gmail.com\\
}

@@

The Business Object Notation (BON) is an analysis and design notation
for object-oriented systems which supports \emph{seamlessness},
\emph{reversibility}, and software \emph{contracting}.  Let us define
these principles precisely and point out why they are important in
VHDL-AMS simulation.

\paragraph{Seamlessness and Reversibility} \emph{Seamlessness} is the
use of a continuous process throughout the software life-cycle.
\emph{Reversibility} is the support for both forward and backward
development process: from analysis to design and implementation, and
back.

>>>>

\author{Joseph R. Kiniry\\
IT University of Copenhagen\\
Copenhagen S., 2300, Denmark\\
kiniry@itu.dk\\
\\
Dragan Stosic\\
UCD CASL: Complex and Adaptive Systems Laboratory and\\
School of Computer Science and Informatics,\\
University College Dublin,\\
Belfield, Dublin 4, Ireland\\
dragan.stosic@gmail.com
}

@@

The Business Object Notation (BON) is an analysis and design notation
for object-oriented systems which supports \emph{seamlessness},
\emph{reversibility}, and software \emph{contracting}.  Let us define
these principles precisely and point out why they are important in
modeling VHDL-AMS.

\paragraph{Seamlessness} \emph{Seamlessness} is the use of a
continuous process throughout the software life-cycle.

\paragraph{Reversibility} \emph{Reversibility} is the support for both
forward and backward development process: from analysis to design and
implementation, and back.
